Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-19 manuscript.Rmd
Updating figures.

```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
# Clear workspace
rm(list=ls())

@@

```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
# Clear workspace
rm(list=ls())

@@

```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

```{r tableArticleSummary, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r plotSmallMultiples}
# Remove 2014 & 2015

@@

```{r articleSummary}
#=======================================
# Create new data file 
#=======================================
library(gridExtra)

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    geom_line(colour=cp[2], size = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("") + 
    ggtitle("Article Count") +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
        scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100))

plot.article.cumulative <- ggplot(articles.df, aes(Year, CumSum, group =1)) + 
    geom_line(colour=cp[2], size = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("") + 
    ggtitle("Cumultative Article Count") +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
        scale_y_continuous(breaks = c(seq(0, 35000, 5000)), limits = c(0, 35000))

@@

n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
    group_by(record.y) %>%
    summarise(Journal.count = n_distinct(record.x))

plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count, group=1)) + 
    geom_line(colour=cp[4], size = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("N") + 
    ggtitle("Journal Count") +
    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
     scale_x_discrete(breaks=seq(1989, 2015, 8))

```{r plotAuthorCount, eval=TRUE}
year.df <- full.df %>%
    filter(attributes == "pubYear") %>%
    select(id = articleID, pubYear = record)

@@

n_authors2$year <- as.factor(c(1989:2013))

@@

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10)) +  
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Authors") +
    xlab("Year") +
    ggtitle("Number of Authors") +
    labs(size = "Standard deviation") +
    labs(colour = "Value") + 
    scale_colour_manual(values = c("#fdb864", "#e66101"))

@@

```{r abstracts}
abstract.df <- filter(full.df, attributes == "abstract")
year.df <- filter(full.df, attributes == "pubYear")
journal.df <- filter(full.df, attributes == "journal")
abstract.df <- left_join(year.df, abstract.df, by = "articleID")
abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
abstract.df$abstract <- tolower(abstract.df$abstract)

@@

year.labs <- as.character(seq(1989,2013, 2))

stacked.plot <- ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("N") + 
    xlab("Year") + 
    labs(fill = "Study type") +
    scale_y_continuous(breaks = seq(0,90, 10))

df <- evidence.summary2

evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .60, colour = "dimgray") + facet_wrap(~studyType) + 
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .015, .005))

######1989########

@@

#df1$studyType <- factor(df1$studyType)
j.order <- unique(df1$journal[order(df1$N.sort, decreasing = FALSE)]) 
df1$journal <- factor(df1$journal, levels = j.order)

@@

journal.evidence.plot <- ggplot(na.omit(df1[df1$journal %in% df1.summarized$journal,]), aes(x = N, y= journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(size = 2.5) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank(), legend.position = "none") + 
    xlim(0, 600) + 
    ylab("Journal") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_x_continuous(breaks = seq(0, 60, 10))

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N)) %>%
    select(-studyType, N) %>%
    distinct(journal, Overall.N, Overall.N.Strength) %>%
    mutate(Prop = Overall.N.Strength / Overall.N)

@@

EBP.plot <- ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0) +
    geom_point(aes(size = Overall.N.Strength)) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
    ylab("Journal") +
    xlab("Proportion") +
    labs(size = "Total number of \nEBP articles published")

```{r pagePlot, eval=TRUE}
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages)) %>%
    group_by(years) %>%
    summarise(
        Median.Pages = median(pages, na.rm=TRUE), 
        Mean.Pages = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10)) +  
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    ylab("Pages") +
    xlab("Year") +
    ggtitle("Article Length") +
    labs(size = "Standard deviation") +
    labs(colour = "Value") + 
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))

>>>>

```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
# Clear workspace
rm(list=ls())

@@

```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
# Clear workspace
rm(list=ls())

@@

```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE, cache=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

```{r tableArticleSummary, eval=TRUE, cache=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r plotSmallMultiples, cache=TRUE}
# Remove 2014 & 2015

@@

```{r plotJournalArticle, cache=FALSE}
#=======================================
# Journals
#=======================================
library(gridExtra)

@@

n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
    group_by(record.y) %>%
    summarise(Journal.count = n_distinct(record.x)) %>%
    mutate(record.y = as.numeric(record.y))

plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count, group=1)) + 
    theme_bw() + 
    geom_line(colour=cp[4], size = 1) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

#=======================================
# Articles
#=======================================

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

```{r plotAuthorCount, eval=TRUE, cache=FALSE}
year.df <- full.df %>%
    filter(attributes == "pubYear") %>%
    select(id = articleID, pubYear = record)

@@

n_authors2$year <- c(1989:2013)

@@

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    theme_bw() + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101") + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Number of Authors") +
    xlab("Year") +
    labs(size = "Standard deviation") +
    labs(colour = "") + 
    scale_colour_manual(values = c("#fdb864", "#e66101")) +
   theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

@@

```{r pagePlot, eval=TRUE, cache=FALSE}
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
    group_by(years) %>%
    summarise(
        Median = median(pages, na.rm=TRUE), 
        Mean.Pages = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

n_authors2$year <- c(1989:2013)

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
    theme_bw() + 
    theme(title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    ylab("Number of Pages") +
    xlab("Year") +
    labs(size = "Standard deviation") +
    labs(colour = "") + 
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

```{r plotStacked, cache=FALSE}
abstract.df <- filter(full.df, attributes == "abstract")
year.df <- filter(full.df, attributes == "pubYear")
journal.df <- filter(full.df, attributes == "journal")
abstract.df <- left_join(year.df, abstract.df, by = "articleID")
abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
abstract.df$abstract <- tolower(abstract.df$abstract)

@@

year.labs <- as.character(seq(1989,2013, 4))

stacked.df <- as.data.frame(xtabs(N~year+studyType, evidence.summary))
stacked.df$year

stacked.plot <- ggplot(stacked.df, 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) +
    theme_bw() +
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
    theme(  legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Number of Articles") + 
    xlab("Year") + 
    labs(fill = "") +
    scale_y_continuous(breaks = seq(0,90, 10)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

df <- evidence.summary2
```

```{r plotProportions, cache=FALSE}
evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
    theme_bw() +
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .03, .005)) 
```

```{r plotClevelandAbsolute}

@@

@@

df1.reduced <- na.omit(df1[df1$journal %in% df1.summarized$journal, ])
df1.reduced <- ungroup(df1.reduced)

df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))

#df1$studyType <- factor(df1$studyType)
j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)]) 
df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)

Text1 <- textGrob("Overall N")
library(gridExtra)

journal.evidence.plot <- ggplot(df1.reduced, 
    aes(x = N, y= journal, group = journal, colour = studyType, shape= studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey90") +
    geom_point(size = 2) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    #facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank(), legend.position = c(.75, .5), 
    legend.title = element_blank(), legend.text = element_text(size = 8)) + 
    xlim(0, 600) + 
    ylab(NULL) +  
    theme(axis.text.x = element_text(hjust = 1, size = 8), axis.ticks = element_blank()) + 
    theme(axis.text.y = element_text(size = 8) ) + 
    scale_x_continuous(breaks = seq(0, 60, 10)) +
    scale_shape_manual(values=c(24, 23, 21, 25))

journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))

```{r plotClevelandRelative}
evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N)) %>%
    select(-studyType, N) %>%
    distinct(journal, Overall.N, Overall.N.Strength) %>%
    mutate(Prop = Overall.N.Strength / Overall.N)

@@

EBP.plot <- ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0) +
    geom_point(aes(size = Overall.N.Strength)) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
    ylab("Journal") +
    xlab("Proportion") +
    labs(size = "Total number of \nEBP articles published") 
```
